Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-17 paper/manuscript.tex
updated Figure 5 legend

@@

\begin{figure}
\centerline{\includegraphics[width=0.8\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\caption{
\label{fig:structures}
{\bf Mutations selected by broad and narrow antibodies.}
(A) For each antibody, the logo plots show the sites where mutations have the largest effect.
Letter heights are proportional to the excess fraction of virions with that mutation that survive antibody, with the proportionality scaled separately for each antibody as indicated by the scale bars.
The structures are colored white to red by the excess fraction surviving for the largest-effect mutation at each site, with each antibody again scaled separately.  
(B) Zoomed-in view of sites of selection from the anti-stalk antibodies C179 and FI6v3, with the same coloring scale for both antibodies.
(C) A phylogenetic tree (not to scale) of HA subtypes, with group 1 in black and group 2 in gray. 
The amino acid at site 38 is indicated. 
Subtypes known to be bound or neutralized by C179 are in green, and subtypes known not to be bound or neutralized are in red.  
\comment{Change coloring in panel C, as red and green are identical to color-blind people. 
Maybe use orange and light blue as in Figure 1.
Also, this figure is too large.
Here I just scaled it all down, but really we want to just shrink panel B. Can you make it a bit smaller with respect to the rest by scaling the figure part by not the text down.
Also, the tree can be made shorter (take up less space) by moving the legend to the right side.}
}
\end{figure}

>>>>

\usepackage[font=small,labelfont=bf]{caption}

@@

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\caption{
\label{fig:structures}
{\bf Mutations selected by broad and narrow antibodies.}
(A) The logo plots show the sites where mutations have the largest effect.
Letter heights are proportional to the excess fraction of virions with that mutation that survive antibody, as indicated by the scale bars.
The structures are colored white to red by the excess fraction surviving for the largest-effect mutation at each site, with each antibody scaled separately.  
(B) Sites of selection from anti-stalk antibodies, with the same coloring scale for both antibodies.
(C) Cladogram of HA subtypes, with group 1 in black and group 2 in gray. 
The amino acid at site 38 is indicated. 
Colors indicate whether a subtype is bound or neutralized by C179 if this has been tested.  
}
\end{figure}
